Understanding the Lomb-Scargle Periodogram

### 2021-09-19 PracticalLombScargle.tex
Update PracticalLombScargle.tex
Small word fix, I think this is what you meant to write.

Because of the close similarity between the classical and Lomb-Scargle periodograms,
the bulk of or previous discussion applies---at least qualitatively---to
periodograms computed with the Lomb-Scargle method.
In particular, reasoning about the effect of window functions on the observed
Lomb-Scargle power spectrum remains qualitatively useful even if it is not
quantitatively precise.

>>>>

Because of the close similarity between the classical and Lomb-Scargle periodograms,
the bulk of our previous discussion applies---at least qualitatively---to
periodograms computed with the Lomb-Scargle method.
In particular, reasoning about the effect of window functions on the observed
Lomb-Scargle power spectrum remains qualitatively useful even if it is not
quantitatively precise.
